\documentclass[linedtoc,
               parskip,
               twoside,
               longdoc,
               11pt,
               noheadingspace,
               accentcolor=tud1d,
               bigchapter,
               %draft,
               colorback]{tudreport}

%% language
\usepackage[english,ngerman]{babel}
%\usepackage[latin1]{inputenc}

\usepackage[ansinew]{inputenc}  % Input-Encodung: ansinew for Windows
\usepackage{microtype} % optischer Randausgleich bei pdflatex mit Zeichendehnung
\usepackage{lmodern}
%% table
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{tabularx}

%% mathematics
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{icomma}

%% misc
\usepackage{paralist}% erweiterte Listenumgebung (z.B. compactitem)
\usepackage{textcomp} % verschiedene Symbole
\usepackage[nottoc, numbib]{tocbibind}
\usepackage[ngerman]{hyperref}
\renewcommand\plparsep{1ex}
\usepackage{enumerate}
\usepackage[stable]{footmisc}
\usepackage{float}
\usepackage{listings}
\usepackage{array}
\usepackage{float}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{todonotes}
\usepackage[acronym,nomain]{glossaries}
\usepackage[american,arrowmos]{circuitikz}
\usepackage[]{appendix}

\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 



\title{Design and Implementation of a Radiation Hardened High Output Current Transconductance Amplifier}
\subtitle{Master thesis submitted by Raghunandan Chakravarthy\\
Supervisor: Sreekesh Lakshminarayanan\\
Start: 21.06.2018 | End: 20.12.2018\\
Department: Integrated Electronic Systems \hspace*{1cm}
| \hfill
Prof. Dr.-Ing. Klaus Hofmann}

%\setinstitutionlogo{"../../Latex Designs/ies_logo"}


\begin{document}
\selectlanguage {english}

%{\setlength{\intextsep}{0pt} % Vertical space above & below [h] floats
%\setlength{\textfloatsep}{0pt} % Vertical space below (above) [t] ([b]) floats
%\setlength{\abovecaptionskip}{3pt}
%\setlength{\belowcaptionskip}{0pt}
% \setlength\itemsep{1em}

%% Titel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\cleardoublepage

%% Vorgeplnkel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{empty}
\pagenumbering{roman}

%% Inhaltsverzeichnis%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{plain}
\addcontentsline{toc}{chapter}{Declaration of Authorship}
\chapter*{Declaration of Authorship}


\textbf{Thesis Statement pursuant to \S\enspace 22 paragraph 7 and \S\enspace23 paragraph 7 of APB TU Darmstadt}

I herewith formally declare that I, Raghunandan Chakravarthy, have written the submitted thesis independently pursuant to \S\enspace22 paragraph 7 of APB TU Darmstadt. I did not use any outside support except for the quoted literature and other sources mentioned in the paper. I clearly marked and separately listed all of the literature and all of the other sources which I employed when producing this academic work, either literally or in content. This thesis has not been handed in or published before in the same or similar form.

I am aware, that in case of an attempt at deception based on plagiarism (\S38 Abs. 2 APB), the thesis would be graded with 5,0 and counted as one failed examination attempt. The thesis may only be repeated once.

In the submitted thesis the written copies and the electronic version for archiving are pursuant to \S\enspace23 paragraph 7 of APB identical in content.


\noindent\rule{17.5cm}{0.4pt}


\textbf{Erkl\"arung zur Abschlussarbeit gem\"a\ss\enspace\S\enspace 22 Abs. 7 und\enspace\S\enspace 23 Abs. 7 APB TU Darmstadt}

Hiermit versichere ich, Raghunandan Chakravarthy, die vorliegende Master-Thesis gem\"a\ss\enspace\S\enspace22 Abs. 7 APB der TU Darmstadt ohne Hilfe Dritter und nur mit den angegebenen Quellen und Hilfsmitteln angefertigt zu haben. Alle Stellen, die Quellen entnommen wurden, sind als solche kenntlich gemacht worden. Diese Arbeit hat in gleicher oder \"ahnlicher Form noch keiner Pr\"ufungsbeh\"orde vorgelegen.

Mir ist bekannt, dass im Falle eines Plagiats (\S38 Abs.2 APB) ein T\"auschungsversuch vorliegt, der dazu f\"uhrt, dass die Arbeit mit 5,0 bewertet und damit ein Pr\"ufungsversuch verbraucht wird. Abschlussarbeiten d\"urfen nur einmal wiederholt werden.

Bei der abgegebenen Thesis stimmen die schriftliche und die zur Archivierung eingereichte elektronische Fassung gem\"a\ss\enspace\S\enspace 23 Abs. 7 APB \"uberein.
\hfill \break

Darmstadt, 20\textsuperscript{th} December 2018 : $\underset{\text{\normalsize(Signature)}}{\underline{\hspace{10cm}}}$

\addcontentsline{toc}{chapter}{Abstract}
\chapter*{Abstract}
%\let\cleardoublepage\clearpage
This thesis details the design and implementation of a radiation hardened high output current transconductance amplifier which can provide currents in the range of $\pm$15mA to $\pm$30mA across a 50$\Omega$ load resistor for a linear input voltage range of $\pm$100mV. An external voltage that controls the bias current is the programmable parameter of the system and it ranges from 150mV to 700mV. The design and impelementation was carried in Cadence Virtuoso Design Environment using XT018 SOI technology from XFAB, to make the design radiation hard. The system consists of two stages - the conventional current mirror based Operational Transconductance Amplifier, which is used as a programmable stage followed by a two-stage Miller compensated Operational Amplifier, which is used as a voltage buffer that generates high currents. Two different design approaches are presented. The first of which is - with the bias current of the first stage being the programmable parameter. The bias current in controlled by a PMOS transistor whose gate voltage is an input of the system. Another design approach is presented with the load being a programmable parameter. For this case, the bias voltage is kept at a constant value of 450mV and the load resistor is varied from 35$\Omega$ to 70$\Omega$. The operating bandwidth of the system is 13MHz. The whole system is intended to be used as part of a Closed-loop Novel DC Current Transformer circuit by providing a feedback current that cancels the change in magnetic field of the ion-beam. As a consequence, the linearity and the sensitivity of the current transformer is improved. The system is simulated at all control settings and across PVT corners to verify its robustness. Simulation results based on schmetic level design are presented.

\addcontentsline{toc}{chapter}{Zusammenfassung}
\chapter*{Zusammenfassung}
In dieser Arbeit wird der Entwurf und die Implementierung eines strahlungsgeh\"arteten Transkonduktanzverst\"arkers mit hohem Ausgangsstrom beschrieben, der Schiene-zu-Schiene-Str\"ome zwischen 15 mA und 30 mA \"uber einen 50$\Omega$ Lastwiderstand f\"ur einen linearen Eingangsspannungsbereich von 100 mV liefern kann. Eine externe Spannung, die den Vorstrom steuert, ist der programmierbare Parameter des Systems und reicht von 150 mV bis 700 mV. Das Design und die Impelementation wurden in Cadence Virtuoso Design Environment unter Verwendung der XT018 SOI-Technologie von XFAB durchgef\"uhrt, um die Designstrahlung zu erschweren. Das System besteht aus zwei Stufen - dem konventionellen, auf einem Stromspiegel basierenden, betrieblichen Transkonduktanzverst\"arker, der als programmierbare Stufe verwendet wird, gefolgt von einem zweistufigen Miller-kompensierten Operationsverst\"arker, der als Spannungspuffer verwendet wird, der hohe Str\"ome erzeugt. Es werden zwei unterschiedliche Designansätze vorgestellt. Die erste davon ist - wobei der Vorspannungsstrom der ersten Stufe der programmierbare Parameter ist. Der Vorspannungsstrom wird von einem PMOS-Transistor gesteuert, dessen Gatespannung ein Eingang des Systems ist. Es werden zwei unterschiedliche Designansätze vorgestellt, wobei die Lastwiederstand ein programmierbarer Parameter ist. In diesem Fall wird die Vorspannung auf einem konstanten Wert von 450 mV gehalten und die Last variiert von 35 $\Omega$ bis 70$\Omega$. Die Betriebsbandbreite des Systems betr\"agt 13 MHz. Das gesamte System ist als Teil eines geschlossenen DC-Stromwandlerkreises mit geschlossenem Regelkreis vorgesehen, indem ein R\"uckkopplungsstrom bereitgestellt wird, der die \"Anderung des Magnetfelds des Ionenstrahls aufhebt. Infolgedessen werden die Linearit\"at und die Empfindlichkeit des Stromwandlers verbessert. Das System wird bei allen Steuereinstellungen und an allen PVT-Ecken simuliert, um seine Robustheit zu \"uberpr\"ufen. Dargestellt werden Simulationsergebnisse basierend auf dem Design der Schmetikebene.

\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgements}
I would like to express my profound gratitude to Prof. Dr.-Ing. Klaus Hofmann for giving me the opportunity to write my Master Thesis at Integrated Electronic Systems institute, Technical University of Darmstadt.
 
To my thesis supervisor M.Sc. Sreekesh Lakshminarayanan, for his constant advice and invaluable feedback that were an integral part of my research. His work ethic and attention to detail is a source of inspiration to say the least. 

To my friends and fellow labmates, for the time we worked together and for all the fun we had in the last six months. A special mention to Khaleelulla Khan Nazeer who shared his abundant knowledge during the crucial phases of my master thesis. 

To my family, for their everlasting unconditional support and moral fibre.

\tableofcontents
\listoffigures
\listoftables
\cleardoublepage

%% Hauptteil %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headings}
\pagenumbering{arabic}

\input{introduction}

\input{theory}

\input{ota}

\input{opamp}

\input{overall}

\input{corners}

\input{conclusion}

\begin{appendices}
\include{appendix}
\end{appendices}

\printglossary[type=acronym, title=Acronyms, toctitle=Acronyms]

\bibliography{ota}
\bibliographystyle{ieeetr}
\end{document}